Pilot study APEROL: questionnaire data

### 2021-01-20 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update questionnaire

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
raw.data<-read.table("./data/short_questionnaire_data_1301211.txt",sep="\t", header=T)

# loading packages
# if a package is not installed on the current machine, it will install it
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)

@@

### Data collection
For the pilot study, we collected questionnaire data from N = `r sum(n_distinct(raw.data$personID))` subjects in `r sum(n_distinct(raw.data$session))` sessions. The questionnaires were answered after each lesson (10min) by an observer, the teacher and the three teachers acting as the class.

@@

```{r overview demographics data table, echo=FALSE}
raw.data %>% # select data
  group_by(session, perspective) %>%
  summarise(N = n_distinct(personID),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age)
            ) %>% 
  knitr::kable(digits = 2)

>>>>

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
raw.data<-read.table("./data/short_questionnaire_data_2001211.txt",sep="\t", header=T)

# loading packages
# install.packages("stringr") # install stringr to use the filter() function with text data
library(stringr)

# if a package is not installed on the current machine, it will install it
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)

@@

### Data collection
For the pilot study, we collected questionnaire data from N = 8 subjects in `r sum(n_distinct(raw.data$session))` sessions. The questionnaires were answered after each lesson (10min) by an observer, the teacher and the three teachers acting as the class.

@@

```{r overview demographics data table, echo=FALSE}

# counting male / female 
sex <- raw.data %>% filter(what == "head")

# # converting column "group" from character into numeric 
# raw.data <- raw.data %>%  mutate(group = as.numeric(as.character(group)))

# demographics, grouped by group, filtered by perspective (N, meanage, max, min age)
raw.data %>% # select data
  filter(perspective == "teacher") %>%
  group_by(group) %>%
  summarise(N = n_distinct(groupID),
            "male" = sum(sex),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age)
            ) %>% 
  knitr::kable(digits = 2)
